Blocking-resistant communication\\through domain fronting

### 2014-07-15 docs/meek.tex
CloudTransport.

% CloudTransport~\cite{cloudtransport}

>>>>

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path rather than the Host header.
For example, in an example S3 URL
\begin{NoHyper}\url{https://s3.amazonaws.com/bucketname/filename}\end{NoHyper},
the censor only gets to ``see'' the generic domain part, \begin{NoHyper}\url{s3.amazonaws.com}\end{NoHyper}.
The path component \begin{NoHyper}\url{/bucketname/filename}\end{NoHyper},
which would reveal that CloudTransport is being used,
cannot be used for blocking because it is encrypted in HTTPS.
